\documentclass[a4paper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{listings}
\lstset{language=C}

\title{{\sc Compiler Construction}\\ TDA282 \\ Submission B}

\author{Andreas Granstr\"om, 870208-8512 \\ \url{andgra@student.chalmers.se} \and Viktor Almqvist, 870624-5613 \\ \url{almqvisv@student.chalmers.se}}
\begin{document}
\maketitle


\section{List of optional extensions}
\begin{itemize}
\item Single-dimensional arrays
\item Multi-dimensional arrays
\end{itemize}

\section{Usage}
\texttt{jlc <source file>} \\ This will produce a binary file
\texttt{a.out} and a LLVM source file (extension \texttt{.ll}) in the
same directory as the supplied source file.

\subsection{Options}
\begin{description}
\item[-t] One can pass the \texttt{-t} option to the compliler
  (ex. \texttt{jlc -t <source file>}), this will print (to standard
  output) the type-annotated abstract syntaxt-tree that the
  typechecker pass to the code-generator. This is mostly used for
  debugging purpuses. Note, this will not comiple the source file.
\item[-nc or --no-compile] Only output the intermediate LLVM-code.
\end{description}

\subsection{Building}
To bulild the compiler, run \texttt{make} in the \texttt{src} directory, it will then produce the \texttt{jlc} binary in the directory ``above''.

The available targets are
\begin{description}
\item[all] Build everything.
\item[jlc] Only build the compiler (not the parser-part).
\item[runtime] Compile the Runtime class.
\item[bnfc] Only build parser-related stuff (Happy and Alex files).
\item[clean] Remove binaries etc.
\item[distclean] Remove all intermediate files, including Happy and Alex files.
\end{description}


\section{The Javalette Language}
After running \texttt{make} in the \texttt{src} dir, view the
\texttt{DocJavalette.txt} file (or build the \texttt{DocJavalette.tex}
file with \LaTeX) for documentation of the language.

\section{Parser issues}
\subsection{shift/reduce}
We have one shift/reduce error in our parser. It is the ``dangling else''
problem, i.e., we have an ambiguity in our grammar. 

Example:
\begin{lstlisting}
  if (A) if (B) ; else;
\end{lstlisting}

As our language is specified, it is ambigious if the \texttt{else}
belongs to \texttt{if (A)} or \texttt{if (B)}.


\end{document}
